```{r}
library("readxl")
library(tidyverse)
library(ggplot2)
crime <- read_excel("D:/STAT6210/crime.xlsx")
crime
#names(crime) <- c("Last Name","First Name"," Age on Date of Crime","Race","Sex","State","Tags","CIU","Guilty Plea","IO","Worst Crime","Occurred","Convicted","Exonerated","Sentence","Death Penalty","DNA only","FC","MWID","F/MFE","P/FA","OM","ILD","State Statute","State Claim Made","0 time","Prem","Pending","Denied","State Award","Amount","Non-Statutory Case Filed","No Time","Unfiled","Dismissed or verdict for D","Pending","Award via Settlement or Verdict for P","Premature","Amount__1","Years Lost")
```

for(i in c(3,11)){
 crime[is.na(crime[,i]), i] <- colMeans(crime[,i], na.rm = TRUE)
}
for(i in c(8,9,10,16:23,25:40)){
 crime[is.na(crime[,i]), i] <- 0
}
crime <- na.omit(crime)
crime=crime%>%
  select(-"Last Name",-"First Name")
#write.csv(crime,file="crime1.csv",row.names=TRUE)

```{r}
crime <- read_csv("D:/STAT6210/crime1.csv")
crime
```

```{r}
#1
a1=crime %>%
     filter(`No Time?`==0) %>%
count()
a1
crime %>%
     filter(`No Time?`==1) %>%
count()
#2
a2=crime %>%
     filter(`No Time?`==0 & `Years Lost`<=1) %>%
count()
a2
#3
a3=crime %>%
     filter(`No Time?`==0 & `Years Lost`>1) %>%
count()
a3
#4
a4_1=crime %>%
  group_by(Race) %>%
count()
a4_1
a4_2=crime %>%
  group_by(Sex) %>%
count()
a4_2
#5
a5_1=crime %>%
     filter(`No Time?`==0) %>%
count(Sex)
a5_1
a5_2=crime %>%
     filter(`No Time?`==0) %>%
count(Race)
a5_2
#6
a6_1=crime %>%
     group_by(Race) %>%
summarise(mean(`Years Lost`))
a6_1
a6_2=crime %>%
     group_by(Sex) %>%
summarise(mean(`Years Lost`))
a6_2
#7
a7_1=crime %>%
  group_by(CIU) %>%
count(`State Claim Made?`==1)
a7_1
a7_2=crime %>%
  group_by(CIU) %>%
count(`State Award?`==1)
a7_2
a7_3=crime %>%
  group_by(CIU) %>%
count(`Non-Statutory Case Filed?`==1)
a7_3
a7_4=crime %>%
  group_by(CIU) %>%
count(`Award via Settlement or Verdict for P`==1)
a7_4
```

```{r}
#8
a8_1=crime %>%
  group_by(`Guilty Plea`) %>%
count(`State Claim Made?`==1)
a8_1
a8_2=crime %>%
  group_by(`Guilty Plea`) %>%
count(`State Award?`==1)
a8_2
a8_3=crime %>%
  group_by(`Guilty Plea`) %>%
count(`Non-Statutory Case Filed?`==1)
a8_3
a8_4=crime %>%
  group_by(`Guilty Plea`) %>%
count(`Award via Settlement or Verdict for P`==1)
a8_4
```
```{r}
#9
a9_1=crime %>%
  group_by(IO) %>%
count(`State Claim Made?`==1)
a9_1
a9_2=crime %>%
  group_by(IO) %>%
count(`State Award?`==1)
a9_2
a9_3=crime %>%
  group_by(IO) %>%
count(`Non-Statutory Case Filed?`==1)
a9_3
a9_4=crime %>%
  group_by(IO) %>%
count(`Award via Settlement or Verdict for P`==1)
a9_4
```
```{r}
#10
a10_1=crime %>%
  group_by(`DNA only`) %>%
count(`State Claim Made?`==1)
a10_1
a10_2=crime %>%
  group_by(`DNA only`) %>%
count(`State Award?`==1)
a10_2
a10_3=crime %>%
  group_by(`DNA only`) %>%
count(`Non-Statutory Case Filed?`==1)
a10_3
a10_4=crime %>%
  group_by(`DNA only`) %>%
count(`Award via Settlement or Verdict for P`==1)
a10_4
```

```{r}
#11
a11_1=crime %>%
  group_by(`Death Penalty?`) %>%
count(`State Claim Made?`==1)
a11_1
a11_2=crime %>%
  group_by(`Death Penalty?`) %>%
count(`State Award?`==1)
a11_2
a11_3=crime %>%
  group_by(`Death Penalty?`) %>%
count(`Non-Statutory Case Filed?`==1)
a11_3
a11_4=crime %>%
  group_by(`Death Penalty?`) %>%
count(`Award via Settlement or Verdict for P`==1)
a11_4
```

```{r}
#12
a12_1=crime %>%
  group_by(`Worst Crime`) %>%
count(`State Claim Made?`==1)
a12_1
a12_2=crime %>%
  group_by(`Worst Crime`) %>%
count(`State Award?`==1)
a12_2
a12_3=crime %>%
  group_by(`Worst Crime`) %>%
count(`Non-Statutory Case Filed?`==1)
a12_3
a12_4=crime %>%
  group_by(`Worst Crime`) %>%
count(`Award via Settlement or Verdict for P`==1)
a12_4
```

```{r}
#13
a13_1=crime %>%
  group_by(Tags) %>%
count(`State Claim Made?`==1)
a13_1
a13_2=crime %>%
  group_by(Tags) %>%
count(`State Award?`==1)
a13_2
a13_3=crime %>%
  group_by(Tags) %>%
count(`Non-Statutory Case Filed?`==1)
a13_3
a13_4=crime %>%
  group_by(Tags) %>%
count(`Award via Settlement or Verdict for P`==1)
a13_4
```
More Complex Inquiries
```{r}
#k=factor(crime$Race)
#g=as.numeric(k)
crime[, 25][is.na(crime[, 25])] <- 0
crime[, 32][is.na(crime[, 32])] <- 0
b1_1=crime %>%
  group_by(Race) %>%
summarise(mean1=mean(`State Claim Made?`),mean2=mean(`Non-Statutory Case Filed?`))

ggplot(mapping = aes(x, y)) +
  geom_bar(data = data.frame(x = b1_1$Race, y = b1_1$mean1), width = 0.8, stat = 'identity') +
  geom_bar(data = data.frame(x = b1_1$Race, y = b1_1$mean2), width = 0.4, stat = 'identity', fill = 'red') +
  theme_classic() + scale_y_continuous(expand = c(0, 0))

#b1_1=crime %>%
#  group_by(Race,Exonerated) %>%
#summarise(mean1=mean(`State Claim Made?`)) %>%
#do(plots=ggplot(data=b1_1) +
#    aes(x=Exonerated, y=mean1) + geom_point())

#ggplot(mapping = aes(x, y)) +
#  geom_point(data = data.frame(x = b1_1$Exonerated, y = b1_1$mean1),colour = 'red') +
#  geom_point(data = data.frame(x = b1_1$Exonerated, y = b1_1$mean2),colour = 'blue') +
#  theme_classic() + scale_y_continuous(expand = c(0, 0))


a8_1
a8_2=crime %>%
  group_by(`Guilty Plea`) %>%
count(`State Award?`==1)
a8_2
a8_3=crime %>%
  group_by(`Guilty Plea`) %>%
count(`Non-Statutory Case Filed?`==1)
a8_3
a8_4=crime %>%
  group_by(`Guilty Plea`) %>%
count(`Award via Settlement or Verdict for P`==1)
a8_4
lm(`Non-Statutory Case Filed?`~.-Sentence,data=crime)
```
crime$Race=as.numeric(crime$Race)
crime$Sex=as.numeric(crime$Sex)
crime$State=as.numeric(crime$State)
crime$Tags=as.numeric(crime$Tags)
crime=crime%>%
  select(-`State Statute?`)
write.csv(crime,file="crime2.csv",row.names=TRUE)

crime <- read_csv("D:/STAT6210/crime1.csv")


```{r}
library("readxl")
library(ggplot2)
library(caret)
library(tree)
library(e1071)
library(MASS)
library(rpart)
library(tree)
library(randomForest)
library(gbm)
library(fastAdaboost)
library(xgboost)
library(ROCR)
library(stringdist)
library(tidyverse)
library(caret)
crime <- read_csv("D:/STAT6210/crime2.csv")
#lm(Amount__1~.-Sentence,data=crime)
crime1=crime%>%
  dplyr::select(-Convicted,-Exonerated,-Sentence,-Occurred)
crime1$`Award via Settlement or Verdict for P`=factor(crime1$`Award via Settlement or Verdict for P`)
names(crime1) <- make.names(names(crime1))
train_val_id <- sample(nrow(crime1), size = floor(nrow(crime1)*.80),replace = FALSE)
train <- crime1[train_val_id,]
test<- crime1[-train_val_id,]
  

temp_ctrl <- trainControl(method = "cv",number = 5) #5-fold CV
temp_grid <- expand.grid(mtry=1:20)

temp_tune <-caret::train(Award.via.Settlement.or.Verdict.for.P~.,data=train,
                         method="rf",
                         trControl=temp_ctrl,
                         tuneGrid=temp_grid,
                         verbose=FALSE,
                         metric="Accuracy"
)
temp_tune #we choose mtry=12

#1
model_rf <- randomForest(Award.via.Settlement.or.Verdict.for.P~.,data=train,mtry=13,ntree=500)
model_rf_pred1 <- model_rf %>% 
predict(test,type = "prob")
rf_pred1=prediction(model_rf_pred1[,2],labels=test$Award.via.Settlement.or.Verdict.for.P)
performance(rf_pred1,"auc")@y.values[[1]]
rf1=model_rf_pred1[,2]

rf.ROC <- performance(rf_pred1,"tpr","fpr")
plot(rf.ROC)
```

```{r}
crime2=crime1%>%
  filter(State.Award.==0 | State.Award.==1)
crime2$State.Award.=factor(crime2$State.Award.)
train_val_id2 <- sample(nrow(crime2), size = floor(nrow(crime2)*.50),replace = FALSE)
train2 <- crime2[train_val_id2,]
val2<- crime2[-train_val_id2,]
test0=crime1%>%
  filter(State.Award.==2)
temp_ctrl <- trainControl(method = "cv",number = 5) #5-fold CV
temp_grid <- expand.grid(mtry=1:30)

temp_tune <-caret::train(State.Award.~.,data=train2,
                         method="rf",
                         trControl=temp_ctrl,
                         tuneGrid=temp_grid,
                         verbose=FALSE,
                         metric="Accuracy"
)
temp_tune #we choose mtry=18

#2
model_rf2 <- randomForest(State.Award.~.,data=train2,mtry=18,ntree=500)
model_rf_pred2 <- model_rf2 %>% 
predict(val2,type = "prob")
rf_pred2=prediction(model_rf_pred2[,2],labels=val2$State.Award.)
performance(rf_pred2,"auc")@y.values[[1]]
rf2=model_rf_pred2[,2]

rf.ROC2 <- performance(rf_pred2,"tpr","fpr")
plot(rf.ROC2)


testPreds <- predict(model_rf2,test0,type = "prob")
```
```{r}
crime
glm.fit <- glm(`Award via Settlement or Verdict for P` ~ .-Occurred-Convicted-Exonerated-Sentence, data = crime, family = binomial)
```

